---
title: "CIND820 DJ0- Big Data Analytics Project||Exploratory Analysis"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
<center> <h1> Broadband Customer Base Churn Datasets </h1> </center>
<center>  <h3> [Motasim Abdo Allah Mahgoob Mohamed Zaki] </h2> </center>
<center> <h3> [course section DJ0 & student number 501086732] </h2> </center>
<center> <h3> [Modeling] </h2> </center>
---
**load the "Clean_Customer_Churn.csv" dataset.**

```{r}
Clean_Customer_Churn=read.csv("C:/1 Motasim/Clean_Customer_Churn.csv",stringsAsFactors = T, sep = ",", na.strings = c("","NA"))

```


# Modeling
#Logistic Regression
#First, split the data into training and testing sets (70% to 30%):
```{r}
library(caret)

train <- createDataPartition(Clean_Customer_Churn$churn, p = 0.7, list = FALSE)
set.seed(2018)
training <- Clean_Customer_Churn[train, ]
testing <- Clean_Customer_Churn[- train, ]
dim(training)
dim(testing)
```


#Fitting the Logistic Regression Model:

```{r}
Logistic_Model <- glm(churn ~ line_stat+ bandwidth+ complaint_cnt+with_phone_service+ tenure_Cat+ secured_revenue+ce_expiry+current_mth_churn, family = binomial(link = "logit"), data = training)
print(summary(Logistic_Model))


```
# from summary: The most-relevant features are Line_stat, Bandwidth, tenure_Cat and with_phone_service



#Assessing the predictive accuracy of the Logistic Regression Model

```{r}
testing$churn <- as.character(testing$churn)
testing$churn[testing$churn == "N"] <- "0"
testing$churn[testing$churn == "Y"] <- "1"
fitted_results <- predict(Logistic_Model, newdata = testing, type = "response")
fitted_results <- ifelse(fitted_results > 0.5, 1, 0)
misClasificError <- mean(fitted_results != testing$churn)
print(paste('Logistic Regression Model Accuracy is', 1- misClasificError))


```
#Confusion Matrix

```{r}
table(testing$churn, fitted_results > 0.5)

```



# Decision Tree visualization

```{r}
#install.packages("party")
library(party)
tree <- ctree(churn ~ with_phone_service+tenure_Cat+bandwidth, training)
plot(tree)

```

#Decsion Tree Confusion Matrix:
```{r}
pred_DT <- predict(tree, testing)
print("The Confusion Matrix of Decision Tree is"); table(Predicted = pred_DT, Actual = testing$churn)


```


#Decision Tree Accuracy
```{r}
pre1 <- predict(tree, training)
step1 <- table(Predicted = pre1, Actual = training$churn)
step2 <- table(Predicted = pred_DT, Actual = testing$churn)
print(paste('The Decision Tree Accuracy is',sum(diag(step2))/sum(step2)))

```

#Naive Bayes Model:
```{r}
#install.packages("naivebayes")
library(naivebayes)
ctrl <- trainControl(method = 'cv',number = 10,classProbs = TRUE,summaryFunction = twoClassSummary)
NB <- train(churn ~ line_stat+ bandwidth+ complaint_cnt+with_phone_service+ tenure_Cat+ secured_revenue+ce_expiry+current_mth_churn, data = training,method = "naive_bayes", trControl = ctrl, metric = "ROC")
NB_pred <- predict(NB,testing)
print("The Confusion Matrix of Naive Bayes is"); 
table(Predicted = NB_pred, Actual = testing$churn)


```

#Naive Bayes Accuracy
```{r}
pred1 <- predict(NB, training)
first_step <- table(Predicted = pred1, Actual = training$churn)
second_step <- table(Predicted = NB_pred, Actual = testing$churn)
print(paste('The Naive Bayes Accuracy is',sum(diag(second_step))/sum(second_step)))

```

#Random Forest

# Random Forest Model
```{r}

gc()
memory.limit(1000000)
#URL<-"randomForest_4.6-14.tar.gz"
#install.packages(URL, repos=NULL, type="source") 
#install.packages("randomForest")
library(randomForest)
RF <- randomForest(churn ~ line_stat+ bandwidth+ complaint_cnt+with_phone_service+ tenure_Cat+ secured_revenue+ce_expiry+current_mth_churn, data = training)
print(RF)
```

# Random Forest Prediction and Confusion Matrix
```{r}
pred_RF <- predict(RF, testing)
#caret::confusionMatrix(pred_rf, testing$Churn)
table(Predicted = pred_RF, Actual = testing$churn)
```


# Random Forest Accuracy
```{r}
predict1 <- predict(tree, training)
step_one <- table(Predicted = predict1, Actual = training$churn)
step_two <- table(Predicted = pred_RF, Actual = testing$churn)
print(paste('The Random Forest Accuracy is',sum(diag(step_two))/sum(step_two)))
```



#Random Forest Feature Importance
```{r}
varImpPlot(RF, sort=T, n.var = 5, main = 'Most important 5 Features')

```

#Balance the data using SMOTE (Synthetic Minority Oversampling Technique)
```{r}
#install.packages( "https://cran.r-project.org/src/contrib/Archive/DMwR/DMwR_0.4.1.tar.gz", repos=NULL, type="source" )
#install.packages(DMwR)
library(DMwR)
New_dataset<- Clean_Customer_Churn[1:100000, c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15)]
#memory.limit(100000)
balanced<- SMOTE(churn ~ . , New_dataset, perc.over = 100)
```


#Verification of balance
```{r}
#install.packages("epiDisplay")
library(epiDisplay)
tab1(balanced$churn,sort.group="decreasing", cum.percent= T)
```

#First, split the data into training2 and testing2 sets (70% to 30%):
```{r}
library(caret)

balanced_train <- createDataPartition(balanced$churn, p = 0.7, list = FALSE)
set.seed(2018)
training2 <- balanced[balanced_train, ]
testing2 <- balanced[- balanced_train, ]
dim(training2)
dim(testing2)
```

#Run the logistic model after balance
```{r}
Logistic_Model2 <- glm(churn ~ line_stat+ bandwidth+ complaint_cnt+with_phone_service+ tenure_Cat+ secured_revenue+ce_expiry+current_mth_churn, family = binomial(link = "logit"), data = training2)
print(summary(Logistic_Model))
```

#Assessing the predictive ability of the Logistic Regression model

```{r}
testing2$churn <- as.character(testing2$churn)
testing2$churn[testing2$churn == "N"] <- "0"
testing2$churn[testing2$churn == "Y"] <- "1"
fitted_results <- predict(Logistic_Model, newdata = testing2, type = "response")
fitted_results <- ifelse(fitted_results > 0.5, 1, 0)
misClasificError <- mean(fitted_results != testing2$churn)
print(paste('Logistic Regression Model Accuracy after balance is', 1- misClasificError))


```



#Install Rtool
```{r}
#write('PATH="${RTOOLS40_HOME}\\usr\\bin;${PATH}"', file = "~/.Renviron", append = TRUE)
#Sys.which("make")

```
























Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
